The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
fix hard coded figure numbers

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure 2) .
<!-- eg this is connecting contexts used to calculate layer similarity -->

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength was consistently weak in summer layers but varied in winter layers at
low number of observations, becoming stable at ~75 observations (Figure
\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
winter layers increased between approximately 10  and 100  observations,
remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
coarse landcover resolution (Figure 4), low numbers of observations were not
sufficient for capturing individuals in all contexts and therefore layer
similarity could not be calculated below ~30 observations for forest,
approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
similarity was not possible to calculate for forage layers because there were no
connected individuals in summer forage. Once sufficient observations were
obtained, layer similarity showed some variability with increasing numbers of
observations for forest and was relatively stable in open layers. Connective
redundancy increased dramatically between ~10 and ~50 observations before
stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

>>>>

Within each layer, we assumed individuals were associating if simultaneous GPS
fixes, i.e., recorded within 5 minutes of each other, were within a given
spatial distance of one another. Typically for ungulates and other gregarious
mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the
chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given
distance formed a contiguous buffer for two or more individuals, even if some
individuals within the buffer were not within the given distance of one another
[@Robitaille_2019]. Group assignment based on the chain rule has previously been
applied to caribou at a distance of 50 m [@Peignier_2019; @Lesmerises_2018]. In
all networks, individual caribou were represented as nodes, associations between
individuals in a given habitat type and season were represented as intralayer
edges, and connections between the same individuals across seasons and within
habitat classes were represented as interlayer edges (Figure \@ref(fig:ml)) .
<!-- eg this is connecting contexts used to calculate layer similarity -->

@@

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength was consistently weak in summer layers but varied in winter layers at
low number of observations, becoming stable at ~75 observations (Figure
\@ref(fig:nobs)a). Layer relevance in the summer was consistently low, but
winter layers increased between approximately 10  and 100  observations,
remaining stable with additional observations (Figure \@ref(fig:nobs)b). Like
coarse landcover resolution (Figure \@ref(fig:lcres)), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below ~30 observations for
forest, approximately ~80 observations for open (Figure \@ref(fig:nobs)c). Layer
similarity was not possible to calculate for forage layers because there were no
connected individuals in summer forage. Once sufficient observations were
obtained, layer similarity showed some variability with increasing numbers of
observations for forest and was relatively stable in open layers. Connective
redundancy increased dramatically between ~10 and ~50 observations before
stabilizing with additional observations included (Figure \@ref(fig:nobs)d).
Given the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.
